NanoMaLy

### 2015-11-20 paper/pldi16-submission/interactive.tex
update graph api/update figure

\paragraph{Visualization State}
%
A \emph{visualization state} $\vstate$ is a \emph{directed graph}
whose vertices are expressions and whose edges are such
that each vertex has at most one predecessor and at most one
successor. In other words, the visualization state looks
like a set of linear lists of expressions as shown in Figure~\ref{fig:FIXTHIS}.
%
The \emph{initial state} is the graph containing a single
edge linking the initial and final expressions.

@@

\paragraph{Update}
Figure~\ref{fig:traversing-graph} shows how we update the state
for each command.
%
The procedure $\findExpr{\vstate}{\cmd}{e}$ traverses the $\tr$
and the current visualization state to compute the new
expression that should be added to the visualization state
and $\updState{\vstate}{\cmd}{e}$ then updates the graph
by inserting the new expression appropriately, using one of
the following functions.
%
$\putBefore{\vstate}{e}{e'}$ (resp. $\putAfter{\vstate}{e}{e'}$)
returns the modified version of $\vstate$ where $e$ is the
immediate predecessor of $e'$ (resp. $e'$ the immediate successor of $e$);
%
$\putRoot{\vstate}{e}$ returns the modified version of $\vstate$ extended
with a new vertex $e$ that has no predecessor or successor, and,
%
$\getRoot{\vstate}{e'}$ be the vertex (expression) obtained
by transitively following the predecessors of $e'$ until a
source vertex.
%
Note that the sub-term edges $\searrow$ allow us to decompose an
expression into a sub-expression and the surrounding context, thus
enabling the \stepintosym\ and \stepoversym\ traversals.

>>>>

\paragraph{Visualization State}
%
A \emph{visualization state} @VState@ is a \emph{directed graph}
whose vertices are expressions and whose edges are such
that each vertex has at most one predecessor and at most one
successor. In other words, the visualization state looks
like a set of linear lists of expressions as shown in Figure~\ref{fig:FIXTHIS}.
%
The \emph{initial state} is the graph containing a single
edge linking the initial and final expressions.

@@

\input{traversals.tex}

\paragraph{Update}
Figure~\ref{fig:traversing-graph} shows how we update the state
for each command.
%
The procedure @findExpr vs cmd e@ traverses the $\tr$
and the current visualization state to compute the new
expression that should be added to the visualization state
and @updState vs cmd e@ then updates the graph
by inserting the new expression appropriately, using one of
the following functions.
%
@putBefore vs e e'@ \hbox{(resp. @putAfter vs e e'@)}
returns the modified version of @vs@ where @e'@ is the
immediate predecessor of @e@ (resp. the immediate successor of @e@);
%
@putRoot vs e@ returns the modified version of @vs@ extended
with a new vertex @e@ that has no predecessor or successor, and,
%
@getRoot vs e@ returns the vertex (expression) obtained
by transitively following the predecessors of @e@ until a
source vertex.
%
@getSubterms vs e@ traverses the sub-term edges to decompose an
expression into a list of sub-expressions paired with their context.
%
@applyCtx vs e ctx@ applies @ctx@ to @e@, traversing the sub-term edges
in reverse to find the super-term of @e@.
%
@findApp vs e@ builds on top of @getSubterms@ to find the first
application sub-term (if any), \ie the first sub-term that looks like
$\eapp{v_1}{v_2}$.
%
@findValue vs e@ traverses the single-step edges to find the final value
that @e@ reduces to.
%
Note that the sub-term edges $\searrow$ allow us to decompose an
expression into a sub-expression and the surrounding context, thus
enabling the \stepintosym\ and \stepoversym\ traversals.
